---
output: 
  html_document:
    keep_md: true
---
R Programming Assignment 2
========================
### *Hristo Hristov*
#### *21 May 2015*

###  Below are two functions that are used to create a special object that stores a matrix and caches its inverse

####  The first function, makeCacheMatrix creates a list containing the functions to:

1. set the matrix
2. get the matrix
3. set the inverse of the matrix
4. get the inverse of the matrix

```{r makeFun}
makeCacheMatrix <- function(x = matrix()) {
    m<-NULL
    set<-function(y){
        x<<-y
        m<<-NULL
    }
    get<-function() x
    setinverse<-function(solve) m<<- solve
    getinverse<-function() m
    list(set=set, get=get,
         setinverse=setinverse,
         getinverse=getinverse)
}
```

#### The following function creates the iverse of the matrix created with the above function. However, it first checks to see if the inverse has already been created. If so, it gets it from the cache and skips the computation. Otherwise, it via the setmean function.
```{r cacheFun}

cacheSolve <- function(x=matrix(), ...) {
    m<-x$getinverse()
    if(!is.null(m)){
        message("getting cached data")
        return(m)
    }
    matrix<-x$get()
    m<-solve(matrix, ...)
    x$setinverse(m)
    m
}
```
#### Testing
```{r testIt}
a<-makeCacheMatrix()# Assign the list to 'a'
a$set(matrix(1:4,2,2))# Generate a matrix
cacheSolve(a)
# Test again to see if it gets it from cache
cacheSolve(a)
```
